Strings functions analysis

### 2022-08-25 article.tex
new table style
table centering
part of bench table added
all let's and you removed

\usepackage[russian]{babel}

@@

    Since popularity is a measurable parameter, let's calculate the number of uses of each string function (see below). Then we denote popularity as a percentage of the number of uses of a certain string function relative to the total number of uses of all string functions. This approach makes it possible to estimate the frequency of string functions usage exactly in the context of correlation with other string functions. \hl{remove all LET'S and YOU}

@@

    The GitHub and Sourcegraph platforms we choose to calculate the number of uses of the functions. This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters.

    However, you should take into account that asking for the number of times a certain word occurs in the code in certain cases will not give a correct result, there are a number of reasons for that.

    \subsubsection{The word is a comment} \hl{}

@@

    \subsubsection{It's a another class function} \hl{}

@@

    For any function (in our case string functions) you can consider such a parameter as its use by other functions. It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.

@@

    In order to define the asymptotics of the different string functions, let us define what a string is. Since we are considering mutable strings, we consider a string to be an array of characters with which we can use write and read operations. This way we can avoid copying for every mutable operation.

@@

@@

    \begin{table*}[]
        \centering
        \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            & \begin{sideways}Popularity\end{sideways}
            & \begin{sideways}Mutual usages\end{sideways}
            & \begin{sideways}Mutable O(?)\end{sideways}
            & \begin{sideways}Immutable O(?)\end{sideways}
            \\ \hline \hline
            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\ \hline

            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\ \hline

            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline

            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\ \hline

            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\ \hline

            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline

% \begin{sideways} \end{sideways}

        \end{tabular}
        \caption{String functions criteria}
        \label{tab:my_label}
    \end{table*}

>>>>

@@

    Since popularity is a measurable parameter, we calculated the number of uses of each string function (see below). Then we denote popularity as a percentage of the number of uses of a certain string function relative to the total number of uses of all string functions. This approach makes it possible to estimate the frequency of string functions usage exactly in the context of correlation with other string functions.

@@

    The GitHub and Sourcegraph platforms we choose to calculate the number of uses of the functions. This platform provides the ability to search for any words or phrases in all GitHub projects, as well as if necessary to specify other parameters. However, we should keep in mind that asking for the number of repetitions of a certain word in the code will in some cases not give the right result, for a number of reasons.

    \subsubsection{The word is a comment}

@@

    \subsubsection{It's a another class function}

@@

    For any function (in our case string functions) we can consider such a parameter as its use by other functions. It is important because it is impossible to exclude a function from the library in case many other functions of the library use it.

@@

    In order to define the asymptotics of the different string functions, we need to define what a string is. Since we are considering mutable strings, we consider a string to be an array of characters with which we can use write and read operations. This way we can avoid copying for every mutable operation.

@@

    \begin{table}[h]
        \begin{tabular}{llll}
            \hline
            & Questions
            & Repositories 100+ stars
            & TIOBE
            \\ \hline

            Python & 1911498 & 39308 & 1 \\

            Java & 1833680 & 20216 & 3 \\

            C++ & 758054 & 13609 & 4 \\ \hline
        \end{tabular}
        \caption{Part of the language criteria table}
    \end{table}

@@

    \begin{table*}
        \begin{tabular}{lllllllllllllll}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            & \begin{sideways}Popularity\end{sideways}
            & \begin{sideways}Mutual usages\end{sideways}
            & \begin{sideways}Mutable O(?)\end{sideways}
            & \begin{sideways}Immutable O(?)\end{sideways}
            \\ \hline

            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            char-at &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\

            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\

            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\

            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions criteria}
        \label{tab:my_label}
    \end{table*}
